\texttt{batman}: BAsic Transit Model cAlculatioN in Python

### 2015-08-07 manuscript/ms.tex
add warning about light travel time

\section{Introduction}
The transit technique has revolutionized the study of exoplanetary systems.  Thanks largely to the \emph{Kepler} mission, thousands of planets have been discovered with this method \citep{rowe15}. These discoveries have yielded transformative constraints on planet occurrence rates over a wide range of planet sizes, orbital periods, and host star properties \citep{borucki11, youdin11, howard12,fressin13, dong13, morton14}. They have also enabled the first estimates of the occurrence of habitable planets \citep{traub12, dressing13, petigura13, kopparapu13, foremanmackey14, dressing15}.  Transit light curves can also reveal planets' atmospheric temperature structure and composition \citep[e.g.][]{seager00, charbonneau02, lecavelier08, sing11, deming13, knutson14a, fraine14, kreidberg15}.  A number of current and planned observational facilities -- including \emph{K2}, \emph{TESS}, \emph{CHEOPS}, \emph{JWST}, and \emph{PLATO} -- will measure precise transit light curves for thousands of exoplanets that will further advance our understanding of planet formation, evolution, and habitability.

@@

\texttt{batman} also provides utilities to calculate the time of periastron and the secondary eclipse time from the other transit parameters, using the method described in \S 3.1 of \cite{eastman13}.

>>>>

\section{Introduction}
The transit technique has revolutionized the study of exoplanetary systems.  Thanks largely to the \emph{Kepler} mission, thousands of planets have been discovered with this method \citep{rowe15}. These discoveries have yielded transformative constraints on planet occurrence rates over a wide range of planet sizes, orbital periods, and host star properties \citep{borucki11, youdin11, howard12,fressin13, dong13, morton14}. They have also enabled the first estimates of the occurrence of habitable planets \citep{traub12, dressing13, petigura13, kopparapu13, foremanmackey14, dressing15}.  Transit light curves can even reveal planets' atmospheric temperature structure and composition \citep[e.g.][]{seager00, charbonneau02, lecavelier08, sing11, deming13, knutson14a, fraine14, kreidberg15}.  A number of current and planned observational facilities -- including \emph{K2}, \emph{TESS}, \emph{CHEOPS}, \emph{JWST}, and \emph{PLATO} -- will measure precise transit light curves for thousands of exoplanets that will further advance our understanding of planet formation, evolution, and habitability.

@@

\texttt{batman} provides utilities to calculate the time of periastron, time of inferior conjunction, and the secondary eclipse time from the other transit parameters, using the method described in \S 3.1 of \cite{eastman13}.  Note however that ``batman`` does not correct for the effects of light travel time.

An additional utility is light curve supersampling, which allows the user to calculate the average value of the light curve over a specified number of evenly spaced points during an exposure.
